---
title: "Final_Report"
author: "Sanghyo Moon"
date: "`r Sys.Date()`"
output: 

  html_document: 
        toc: true
        toc_float: true
        toc_depth: 3
        number_sections: true

        fig_width: 9 
        fig_height: 4
        fig_align: "center"
        fig_caption: true
        
        highlight: pygments
        theme: cerulean
        
        keep_md: true
        
        code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

knitr::write_bib(c("evpi","decisionSupport","ggplot2"), "packages.bib")
```


```{r Import Libraries, echo=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(decisionSupport)
library(readr)
library(tidyverse)
library(sf)
library(kableExtra)
library(evpi)
```

# Location of Partners
These partners provide information, which is directly related to the Decision Analysis. 

However, we have also two partners in Bayern

```{r Mapping,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

partners <- data.frame(Partner = c("1", "2", "3", "4", "5", "6", "7", "8", "9","10"),
                Latitude = c("50.905235", "49.9847", "50.7292847", "48.2233187", "50.1086989", 
                             "51.4425624","51.0322072", "51.4375832", "51.3206", "51.0322072"),
                Longitude = c("6.4042735", "7.96835", "7.0731143", "11.592294", "11.4510019", 
                              "6.266977","6.6134963", "6.3253844", "6.4951", "6.6134963")
                )


# !reading the shapefile (the map)
# shapefiles are from eurostat, there are different versions, here i am using the version of 2021
# Source: https://ec.europa.eu/eurostat/de/web/gisco/geodata/statistical-units/territorial-units-statistics

shape <- read_sf(dsn = "map/German_Geo/NUTS_RG_20M_2021_3035.shp")
shape <- shape %>% dplyr::filter(CNTR_CODE == "DE",LEVL_CODE == 3)
names(shape)[4] <- "kreis"

# !transforming the soil point crs into the shapefile crs
maps <- partners %>% st_as_sf(coords = c("Longitude", "Latitude"), 
                               crs="+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
  st_transform(st_crs(shape))

# !checking if the points are inside the polygons of our Nuts3 Shapefile
partner_maps <- st_join(maps, shape)
partner_maps_NRW_HS <- partner_maps %>%
    filter(NUTS_ID != "DE21H")%>%
  filter(NUTS_ID != "DE24B")

# !filtering only points that are within NRW & Hessen
# NUTS code for NRW is DEA, Hessen is DEB
shape_NRW <- filter(shape, str_detect(NUTS_ID, "^DEA"))
shape_HS <- filter(shape, str_detect(NUTS_ID, "^DEB"))


# Ensure `shape_NRW` & `shape_HS` is only at the state level by merging county boundaries
Boundary_NRW <- shape_NRW %>%
  summarise(geometry = st_union(geometry))  # Dissolve internal county borders

Boundary_HS <- shape_HS %>%
  summarise(geometry = st_union(geometry))  # Dissolve internal county borders


#combine boundaries 
Boundary_Combined <- rbind(Boundary_NRW, Boundary_HS)


# create plot
Project_partners <- ggplot(Boundary_Combined) +
  geom_sf(data = Boundary_Combined, fill = "#e0e0e0", color = "#999999") + # color = "#999999" with boundary
  geom_sf(data = partner_maps_NRW_HS, aes(color = "Project Partners"),
          show.legend = TRUE, size = 3) +
  scale_color_manual(values = c("Project Partners" = "#fa744b")) +
  theme_bw() +
  theme(legend.position = "bottom", 
        legend.box="horizontal",
        legend.key.width= unit(2, 'cm'),
        strip.text = element_text(size = 11, face = "bold"), 
        legend.text = element_text(size = 12),
        legend.title.align = 0.5,
        legend.title = element_text(size = 14, face = "bold"))+
  guides(color=guide_legend(title="Locations"), font = 2)

Project_partners
```


# Data reading 
## Yield Data from LWK

```{r Yield_LWK, eval=F, echo=T}

# calculation of yield per square meters and per season with 95% convidence interval

Yield <- read_csv("data/Yield.csv")

# calculating CV and if there are two variables for a treatment then calculate average of the CV
Yield_clean <- Yield[ , !grepl("lose", names(Yield), ignore.case = TRUE) ]
Yield_clean_2 <- Yield_clean[ , -((ncol(Yield_clean)-2):ncol(Yield_clean)) ]
cv <- apply(Yield_clean_2, 2, function(x) sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE))
cv_rounded <- round(cv, 3)
cv_percent <- cv * 100



# calculate sd 
sds <- apply(Yield_clean_2, 2, sd, na.rm = TRUE)
number <- Yield_clean_2%>% summarise(across(1:12, ~sum(!is.na(.))))
long_data <- number %>%pivot_longer(cols = 1:12, names_to = "Variable", values_to = "Value")
# calculate SEM standard error of mean
SEMs <- sds / sqrt(long_data$Value)

# Sum/13.8qm -> yield/qm/season 
  # 180qm Haus, 13 Rinnen, ... 
Summary_Yield <- colSums(Yield_clean_2, na.rm = TRUE)
column_sums_qm <- Summary_Yield / 13.8



# data frame
sum_qm_df <- data.frame(
  Column = names(column_sums_qm),
  sum_qm = column_sums_qm, 
  cv = cv,
  cv_percent = cv_percent,
  sd = sds,
  n = long_data$Value,
  SEM = SEMs)

# calculate lower and upper value with 90% confidence interval
# Set Z-score for 90% confidence level
z_score <- 1.645

# Calculate lower and upper bounds of the 90% confidence interval
sum_qm_df$lower_90 <- sum_qm_df$sum_qm - z_score * sum_qm_df$SEM  # lower bound, clipped at 0
sum_qm_df$upper_90 <- sum_qm_df$sum_qm + z_score * sum_qm_df$SEM           # upper bound


# arrange the data frame
# Subset only the rows for KK_Tross and KK_Tross_1
kk_rows <- sum_qm_df[sum_qm_df$Column %in% c("KK_Tross", "KK_Tross_1"), ]
ks_rows <- sum_qm_df[sum_qm_df$Column %in% c("KS_Tross", "KS_Tross_3"), ]
kh_rows <- sum_qm_df[sum_qm_df$Column %in% c("KH_Tross", "KH_Tross_5"), ]

# Calculate mean for selected numeric columns
kk_means <- colMeans(kk_rows[, c("sum_qm", "cv", "sd", "lower_90", "upper_90")])
ks_means <- colMeans(ks_rows[, c("sum_qm", "cv", "sd", "lower_90", "upper_90")])
kh_means <- colMeans(kh_rows[, c("sum_qm", "cv", "sd", "lower_90", "upper_90")])

# Update the KK_Tross row with the new mean values
sum_qm_df[sum_qm_df$Column == "KK_Tross", c("sum_qm", "cv", "sd", "lower_90", "upper_90")] <- kk_means
sum_qm_df[sum_qm_df$Column == "KS_Tross", c("sum_qm", "cv", "sd", "lower_90", "upper_90")] <- ks_means
sum_qm_df[sum_qm_df$Column == "KH_Tross", c("sum_qm", "cv", "sd", "lower_90", "upper_90")] <- kh_means

# Remove the KK_Tross_1 row
sum_qm_df_2 <- sum_qm_df[sum_qm_df$Column != "KK_Tross_1",]
sum_qm_df_2 <- sum_qm_df_2[sum_qm_df_2$Column != "KS_Tross_3",]
sum_qm_df_3 <- sum_qm_df_2[sum_qm_df_2$Column != "KH_Tross_5",]
# use the value for a base line. 

#reorder by column index
sum_qm_df_3 <- sum_qm_df_3[, c(1,8,2,9,3,4,5,6,7)]

sum_qm_df_4 <- sum_qm_df_3 %>% round(sum_qm_df_3[2:9], 3)

kable(sum_qm_df_4) %>%
  kable_styling("striped", position = "left",font_size = 10)%>%
  scroll_box(height = "200px")



write.csv(sum_qm_df_4, "data/calculated_yield.csv", row.names = FALSE)

```



- Yield data: confident interval 90% here for min and max from LWK_Data

- once CVs and Yields are clear, then add into the input table. 

- Mean value of two yield data if there are 2 different yield.

# function for the mc simulation
```{r include=FALSE}

Priming_function <- function(x, varnames){
  #Leistung
  Yield_K_K <- vv(Yield_type_1, var_CV_Yield_type_1, n_years)
  Yield_K_H <- vv(Yield_type_2, var_CV_Yield_type_2, n_years)
  Yield_K_S <- vv(Yield_type_3, var_CV_Yield_type_3, n_years)
  Yield_H_K <- vv(Yield_type_4, var_CV_Yield_type_4, n_years)
  Yield_H_H <- vv(Yield_type_5, var_CV_Yield_type_5, n_years)
  Yield_H_S <- vv(Yield_type_6, var_CV_Yield_type_6, n_years)
  Yield_S_K <- vv(Yield_type_7, var_CV_Yield_type_7, n_years)
  Yield_S_H <- vv(Yield_type_8, var_CV_Yield_type_8, n_years)
  Yield_S_S <- vv(Yield_type_9, var_CV_Yield_type_9, n_years)
  
  TomatenPreis <-vv(Tomaten_Preis, var_CV_Tomaten_Preis, n_years)
  
  # Leistung
  Leistung_K_K <- Yield_K_K+TomatenPreis
  Leistung_K_H <- Yield_K_H + TomatenPreis
  Leistung_K_S <- Yield_K_S + TomatenPreis
  Leistung_H_K <- Yield_H_K + TomatenPreis
  Leistung_H_H <- Yield_H_H + TomatenPreis
  Leistung_H_S <- Yield_H_S + TomatenPreis
  Leistung_S_K <- Yield_S_K + TomatenPreis
  Leistung_S_H <- Yield_S_H + TomatenPreis
  Leistung_S_S <- Yield_S_S + TomatenPreis
  
  #Ausgabe
  #Direkt Kosten & Arbeitskosten
  Kosten_ohne_Priming <- Saatgut + Jungepflanzen + 
    Substrat + Energie_therm + Energie_elek + CO2_H2O_Due + Kordel +
    Hummel_Nutzlinge + PSM_chem + Heackseln_Entsorgung + Desinfektion +
    Versicherung + Arbeit
  
  Kosten_mit_Priming <- Saatgut + Jungepflanzen_Priming +
    Substrat + Energie_therm + Energie_elek + CO2_H2O_Due + Kordel +
    Hummel_Nutzlinge + PSM_chem + Heackseln_Entsorgung + Desinfektion +
    Versicherung + Arbeit
  
  
  ## Total_ Gewinn_Kosten ##
  
  
  Result_K_K <- Leistung_K_K - Kosten_ohne_Priming
  Result_K_H <- Leistung_K_H - Kosten_ohne_Priming
  Result_K_S <- Leistung_K_S - Kosten_ohne_Priming
  Result_H_K <- Leistung_H_K - Kosten_mit_Priming
  Result_H_H <- Leistung_H_H - Kosten_mit_Priming
  Result_H_S <- Leistung_H_S - Kosten_mit_Priming
  Result_S_K <- Leistung_S_K - Kosten_mit_Priming
  Result_S_H <- Leistung_S_H - Kosten_mit_Priming
  Result_S_S <- Leistung_S_S - Kosten_mit_Priming
  
  
  #NPV calculate
  
  NPV_K_K <- discount(Result_K_K, discount_rate, calculate_NPV = T)
  NPV_K_H <- discount(Result_K_H, discount_rate, calculate_NPV = T)
  NPV_K_S <- discount(Result_K_S, discount_rate, calculate_NPV = T)
  NPV_H_K <- discount(Result_H_K, discount_rate, calculate_NPV = T)
  NPV_H_H <- discount(Result_H_H, discount_rate, calculate_NPV = T)
  NPV_H_S <- discount(Result_H_S, discount_rate, calculate_NPV = T)
  NPV_S_K <- discount(Result_S_K, discount_rate, calculate_NPV = T)
  NPV_S_H <- discount(Result_S_H, discount_rate, calculate_NPV = T)
  NPV_S_S <- discount(Result_S_S, discount_rate, calculate_NPV = T)
  
  
  return(list(K_K_NPV = NPV_K_K,
              K_H_NPV = NPV_K_H, 
              K_S_NPV = NPV_K_S,
              H_K_NPV = NPV_H_K, 
              H_H_NPV = NPV_H_H,
              H_S_NPV = NPV_H_S,
              S_K_NPV = NPV_S_K,
              S_H_NPV = NPV_S_H,
              S_S_NPV = NPV_S_S,
              
              NPV_K_H_NPV_K_K = NPV_K_H - NPV_K_K,
              NPV_K_S_NPV_K_K = NPV_K_S - NPV_K_K,
              NPV_H_K_NPV_K_K = NPV_H_K - NPV_K_K,
              NPV_S_K_NPV_K_K = NPV_S_K - NPV_K_K,
              NPV_H_H_NPV_K_H = NPV_H_H - NPV_K_H,
              NPV_S_H_NPV_K_H = NPV_S_H - NPV_K_H,
              NPV_H_S_NPV_K_S = NPV_H_S - NPV_K_S,
              NPV_S_S_NPV_K_S = NPV_S_S - NPV_K_S,
              
              Cashflow_KH_KK = Result_K_H - Result_K_K,
              Cashflow_KS_KK = Result_K_S - Result_K_K,
              Cashflow_HK_KK = Result_H_K - Result_K_K,
              Cashflow_SK_KK = Result_S_K - Result_K_K,
              Cashflow_HH_KH = Result_H_H - Result_K_H,
              Cashflow_SH_KH = Result_S_H - Result_K_H,
              Cashflow_HS_KS = Result_H_S - Result_K_S,
              Cashflow_SS_KS = Result_S_S - Result_K_S
              
  )) 
}
```

# scenario_mc
This function is a wrapper around the mc_Simulation function that facilitates implementation of scenarios. The standard mc_Simulation function only allows specifying one set of estimates (i.e. distribution, lower and upper bounds) for each random variable. This is inconvenient when we want to run simulations for heterogeneous populations that include subsets with particular characteristics, e.g. small and large farms. It may then make sense to specify separate distributions for input variables for each of the subsets. The scenario_mc function facilitates this.

# Smaller farms

```{r function, include=FALSE}

scenarios_0<-read.csv("data/scenarios.csv", fileEncoding = "UTF-8-BOM")
scenarios <- scenarios_0[, -ncol(scenarios_0)]
s_farm<-scenarios[,c(1,2,3)]

s_farm_Priming_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/baseline.csv"),
                                      scenarios = s_farm,
                                      model_function = Priming_function,
                                      numberOfModelRuns = 50000,
                                      functionSyntax = "plainNames")

```

## distributions of the mc simulation
```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}


no_stress_s_farm <- plot_distributions(mcSimulation_object = s_farm_Priming_scenarios, 
                   vars = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   new_names = c("no priming","heat priming","salt priming"),
                   base_size = 10,
                   legend.position = "none",
                   x_axis_name = "Net Present Value [€/m2]") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress for Smaller Farms",
       fill = "Decision Options")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "bottom",)+
  scale_fill_manual(
    values = c("no priming" = "#009E73", "heat priming" = "tomato", "salt priming" = "#56B4E9"),
    breaks = c("no priming", "heat priming",  "salt priming")  # << THIS controls legend order
  )


no_stress_s_farm_salt <- plot_distributions(mcSimulation_object = s_farm_Priming_scenarios, 
                   vars = c("K_K_NPV","S_K_NPV"),
                   method = "boxplot", 
                   old_names = c("K_K_NPV","S_K_NPV"),
                   new_names = c("no priming","salt priming"),
                   base_size = 10,
                   legend.position = "none",
                   x_axis_name = "Net Present Value [€/m2]") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress for Smaller Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no priming" = "#009E73", "salt priming" = "#56B4E9"),
    breaks = c("no priming", "salt priming")  # << THIS controls legend order
  )


no_priming_s_farm <- plot_distributions(mcSimulation_object = s_farm_Priming_scenarios, 
                   vars = c("K_K_NPV","K_H_NPV","K_S_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","K_H_NPV","K_S_NPV"),
                   new_names = c("no stress","heat stress","salt stress"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "NPV Distribution with No Prming \nand Different Stresses for Smaller Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no stress" = "#009E73", "salt stress" = "#56B4E9", "heat stress" = "tomato"),
    breaks = c("no stress", "salt stress", "heat stress")  # << THIS controls legend order
  )



heat_stress_s_farm <- plot_distributions(
  mcSimulation_object = s_farm_Priming_scenarios, 
  vars = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for Smaller Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "heat priming" = "tomato", "salt priming" = "#56B4E9"),
    breaks = c("no priming", "heat priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order


heat_stress_s_farm_heat <- plot_distributions(
  mcSimulation_object = s_farm_Priming_scenarios, 
  vars = c("K_H_NPV", "H_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV", "H_H_NPV"),
  new_names = c("no priming", "heat priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for Smaller Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "heat priming" = "tomato"),
    breaks = c("no priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming","no priming"))  # << critical: y-axis order


heat_stress_s_farm_salt <- plot_distributions(
  mcSimulation_object = s_farm_Priming_scenarios, 
  vars = c("K_H_NPV",  "S_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV",  "S_H_NPV"),
  new_names = c("no priming",  "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for Smaller Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73",  "salt priming" = "#56B4E9"),
    breaks = c("no priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c( "salt priming","no priming"))  # << critical: y-axis order



salt_stress_s_farm <- plot_distributions(
  mcSimulation_object = s_farm_Priming_scenarios, 
  vars = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  method = 'boxplot', 
  old_names = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for Smaller Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "heat priming" = "tomato", "salt priming" = "#56B4E9"),
    breaks = c("no priming", "heat priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order



salt_priming_s_farm <- plot_distributions(mcSimulation_object = s_farm_Priming_scenarios, 
                   vars = c("S_K_NPV","S_H_NPV","S_S_NPV"),
                   method = 'boxplot', 
                   old_names = c("S_K_NPV","S_H_NPV","S_S_NPV"),
                   new_names = c("no stress","heat stress","salt stress"),
                   base_size = 10,
                   colors = c("tomato","#009E73","#56B4E9"),
                   legend.position = "none") +
  labs(title = "NPV Distribution with Salt Prming \nand Different Stresses for Smaller Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no stress" = "#009E73", "salt stress" = "#56B4E9", "heat stress" = "tomato"),
    breaks = c("no stress", "salt stress", "heat stress")) + # order y-axis and legend
  scale_y_discrete(limits = c(  "heat stress","salt stress","no stress"))  # << critical: y-axis order




cashflow_KK_HK_s_farm <- plot_cashflow(mcSimulation_object = s_farm_Priming_scenarios, 
              cashflow_var_name = "Cashflow_H_K",
              facet_labels = "Cash Flow Comparison Between No Priming \nand Heat Priming for Smaller Farms" )


cashflow_KK_SK_s_farm <- plot_cashflow(mcSimulation_object = s_farm_Priming_scenarios, 
              cashflow_var_name = "Cashflow_S_K",
              facet_labels ="Cash Flow Comparison Between No Priming \nand Salt Priming for Smaller Farms" )




```

## EVPI & VIP for smaller farms

### EVPI
```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
### Value of Information (VoI) analysis ###

#here we subset the outputs from the mcSimulation function (y) by selecting the correct variables
# choose this carefully and be sure to run the multi_EVPI only on the variables that the you want
#EVPI = (EOL : Expected Opportunity Loss)

# make a individual data.frame from the scenario data. 

# Monte carlo inputs
s_farm_list2 <- s_farm_Priming_scenarios[[2]]
#remove the row with character (Farm_1, Farm_2...)
s_farm_list2 <- s_farm_list2[, -36]

# Monte Carlo outputs
s_farm_list1 <- s_farm_Priming_scenarios[[1]]
# choose only NPV
s_farm_list1 <- s_farm_list1[1:7]


```

### VIP


```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
#PLS

Priming_scenarios_sfarm <- s_farm_Priming_scenarios
Priming_scenarios_sfarm$x<-Priming_scenarios_sfarm$x[,which(!colnames(Priming_scenarios_sfarm$x)=="Scenario")]

#legend_table<-read.csv("Final_Report/baseline.csv", fileEncoding = "UTF-8-BOM")

#PLS for Heat priming - no priming under control
pls_out_sfarm<-plsr.mcSimulation(object=Priming_scenarios_sfarm, 
                                 resultName = names(Priming_scenarios_sfarm$y)[12])


coeff1 <- pls_out_sfarm[["coefficients"]][,,1]
scale  <- pls_out_sfarm[["scale"]]



```

### EVPI & VIP no priming & heat priming wihtout stress treatment

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}


# vergleich kk zu HK
s_farm_list14 <- s_farm_list1[c(1,4)]

s_farm_EVPI14_0 <-  evpi::multi_evppi(s_farm_list2, s_farm_list14)

s_farm_EVPI14 <- data.frame(
  Variable = colnames(s_farm_list2),
  EVPI = s_farm_EVPI14_0
)


s_farm_EVPI_14 <- s_farm_EVPI14[1:26, ]

VIP_table_HK_KK_sfarm_14 <- data.frame(
  name = names(scale),
  VIP = as.numeric(scale),
  coefficient = as.numeric(coeff1),
EVPI = as.numeric(s_farm_EVPI_14$EVPI))

VIP_table_HK_KK_sfarm14 <- VIP_table_HK_KK_sfarm_14[-26, ]



```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset <- subset(VIP_table_HK_KK_sfarm14,VIP_table_HK_KK_sfarm14$VIP>=0.8)
pls_subset <- subset(VIP_table_HK_KK_sfarm14,VIP_table_HK_KK_sfarm14$EVPI>=1)
pls_subset$Category[pls_subset$coefficient > 0] = "cadetblue"
pls_subset$Category[pls_subset$coefficient < 0] = "firebrick"
pls_subset$Category[pls_subset$VIP < 1] ="grey"
pls_dat <- as.data.frame(pls_subset)
name_mapping <- c(
  "Yield_type_4" = "Yield of Heat primed tomato [kg/m2]",
  "Yield_type_7" = "Yield of Salt primed tomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed tomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat$X <- name_mapping[pls_dat$name]

p <- ggplot(pls_dat,aes(x=pls_dat$name,y=pls_dat$VIP))+
  geom_bar(aes(fill=pls_dat$Category),stat ="identity")+
  ggtitle("Variable Importance")+
  ylab("VIP scores")+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q <-  ggplot(data = pls_dat, aes(x = pls_dat$X, y = pls_dat$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle("Value of Information") +
  ylab("EVPI")+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()
g.mid <- ggplot(pls_dat,aes(x=1,y=pls_dat$X))+geom_text(aes(label=pls_dat$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat$X))+
  ggtitle("")+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1 <- ggplot_gtable(ggplot_build(p))
gg2 <- ggplot_gtable(ggplot_build(q))
gg.mid <- ggplot_gtable(ggplot_build(g.mid))
gg_KK_HH_sfarm <- cowplot::plot_grid(gg1,gg.mid,gg2, ncol = 3, align = "h")


```



### EVPI & VIP no priming & salt priming wihtout stress treatment

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

s_farm_list17 <- s_farm_list1[c(1,7)]

s_farm_EVPI17 <-  evpi::multi_evppi(s_farm_list2, s_farm_list17)

s_farm_EVPI17 <- data.frame(
  Variable = colnames(s_farm_list2),
  EVPI = s_farm_EVPI17
)


s_farm_EVPI_17 <- s_farm_EVPI17[1:26, ]

VIP_table_SK_KK_sfarm_17 <- data.frame(
  name = names(scale),
  VIP = as.numeric(scale),
  coefficient = as.numeric(coeff1),
EVPI = as.numeric(s_farm_EVPI_17$EVPI))

VIP_table_SK_KK_sfarm17 <- VIP_table_SK_KK_sfarm_17[-26, ]



```

graph

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset <- subset(VIP_table_SK_KK_sfarm17,VIP_table_SK_KK_sfarm17$VIP>=0.8)
pls_subset <- subset(VIP_table_SK_KK_sfarm17,VIP_table_SK_KK_sfarm17$EVPI>=1.1)
pls_subset$Category[pls_subset$coefficient > 0] = "cadetblue"
pls_subset$Category[pls_subset$coefficient < 0] = "firebrick"
pls_subset$Category[pls_subset$VIP < 1] ="grey"
pls_dat_17 <- as.data.frame(pls_subset)
name_mapping <- c(
  "Yield_type_4" = "Yield of Heat primed tomato [kg/m2]",
  "Yield_type_7" = "Yield of Salt primed tomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed tomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_17$X <- name_mapping[pls_dat_17$name]

p <- ggplot(pls_dat_17,aes(x=pls_dat_17$name,y=pls_dat_17$VIP))+
  geom_bar(aes(fill=pls_dat_17$Category),stat ="identity")+
  ggtitle("Variable Importance")+
  ylab("VIP scores")+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q <-  ggplot(data = pls_dat_17, aes(x = pls_dat_17$X, y = pls_dat_17$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle("Value of Information") +
  ylab("EVPI")+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()
g.mid <- ggplot(pls_dat_17,aes(x=1,y=pls_dat_17$X))+geom_text(aes(label=pls_dat_17$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_17$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_17$X))+
  ggtitle("")+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1 <- ggplot_gtable(ggplot_build(p))
gg2 <- ggplot_gtable(ggplot_build(q))
gg.mid <- ggplot_gtable(ggplot_build(g.mid))
gg_SK_KK_sfarm <- cowplot::plot_grid(gg1,gg.mid,gg2, ncol = 3, align = "h")


```



# Larger farms


```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}


scenarios_0<-read.csv("data/scenarios.csv", fileEncoding = "UTF-8-BOM")

b_farm<-scenarios_0[,c(1,2,4,5)]

b_farm_Priming_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/baseline.csv"),
                                      scenarios = b_farm,
                                      model_function = Priming_function,
                                      numberOfModelRuns = 50000,
                                      functionSyntax = "plainNames")
```

## distributions of the mc simulation
```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
no_stress_bfarm <- plot_distributions(mcSimulation_object = b_farm_Priming_scenarios, 
                   vars = c("K_K_NPV","S_K_NPV","H_K_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   new_names = c("no priming","heat priming","salt priming"),
                   base_size = 10,
                   colors = c("tomato","#009E73","#56B4E9"),
                   legend.position = "none") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress for Larger Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9", "heat priming" = "tomato"),
    breaks = c("no priming",  "salt priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order



heat_stress_s_farm <- plot_distributions(
  mcSimulation_object = b_farm_Priming_scenarios, 
  vars = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for bigger Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9", "heat priming" = "tomato"),
    breaks = c("no priming",  "salt priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order


salt_stress_b_farm <- plot_distributions(
  mcSimulation_object = b_farm_Priming_scenarios, 
  vars = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  method = 'boxplot', 
  old_names = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for bigger Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9", "heat priming" = "tomato"),
    breaks = c("no priming",  "salt priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order


no_priming_bfarm <- plot_distributions(mcSimulation_object = b_farm_Priming_scenarios, 
                   vars = c("K_K_NPV","K_S_NPV","K_H_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","K_H_NPV","K_S_NPV"),
                   new_names = c("no stress","heat stress","salt stress"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "NPV Distribution with No Prming \nand Different Stresses for Larger Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no stress" = "#009E73", "salt stress" = "#56B4E9", "heat stress" = "tomato"),
    breaks = c("no stress", "salt stress", "heat stress")) + # order y-axis and legend
  scale_y_discrete(limits = c(  "heat stress","salt stress","no stress"))  # << critical: y-axis order



heat_priming_bfarm <- plot_distributions(mcSimulation_object = b_farm_Priming_scenarios, 
                   vars = c("H_K_NPV","H_H_NPV","H_S_NPV"),
                   method = 'boxplot', 
                   old_names = c("H_K_NPV","H_H_NPV","H_S_NPV"),
                   new_names = c("no stress","heat stress","salt stress"),
                   base_size = 10,
                   colors = c("tomato","#009E73","#56B4E9"),
                   legend.position = "none") +
  labs(title = "NPV Distribution with Heat Prming \nand Different Stresses for Larger Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no stress" = "#009E73", "salt stress" = "#56B4E9", "heat stress" = "tomato"),
    breaks = c("no stress", "salt stress", "heat stress")) + # order y-axis and legend
  scale_y_discrete(limits = c(  "heat stress","salt stress","no stress"))  # << critical: y-axis order


ggsave( paste0("graphs/no_priming_bfarm",".tiff"), no_priming_bfarm, 
        width = 12, height = 8, units = 'cm', dpi = 750, compression = "lzw")


salt_priming_bfarm <- plot_distributions(mcSimulation_object = b_farm_Priming_scenarios, 
                   vars = c("S_K_NPV","S_H_NPV","S_S_NPV"),
                   method = 'boxplot', 
                   old_names = c("S_K_NPV","S_H_NPV","S_S_NPV"),
                   new_names = c("no stress","heat stress","salt stress"),
                   base_size = 10,
                   colors = c("tomato","#009E73","#56B4E9"),
                   legend.position = "none") +
  labs(title = "NPV Distribution with Salt Prming \nand Different Stresses for Larger Farms")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c("no stress" = "#009E73", "salt stress" = "#56B4E9", "heat stress" = "tomato"),
    breaks = c("no stress", "salt stress", "heat stress")) + # order y-axis and legend
  scale_y_discrete(limits = c(  "heat stress","salt stress","no stress"))  # << critical: y-axis order




cashflow_KK_HK_bfarm <- plot_cashflow(mcSimulation_object = s_farm_Priming_scenarios, 
              cashflow_var_name = "Cashflow_H_K",
              facet_labels = "Cash Flow Comparison Between No Priming \nand Heat Priming for Larger Farms" )



cashflow_KK_SK_bfarm <- plot_cashflow(mcSimulation_object = s_farm_Priming_scenarios, 
              cashflow_var_name = "Cashflow_S_K",
              facet_labels ="Cash Flow Comparison Between No Priming \nand Salt Priming for Larger Farms" )



```

## EVPI & VIP for smaller farms

### EVPI
```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}


# make a individual data.frame from the scenario data. 

# Monte carlo inputs
b_farm_list2 <- b_farm_Priming_scenarios[[2]]
#remove the row with character (Farm_1, Farm_2...)

b_farm_list2 <- b_farm_list2[, -36]
# Monte Carlo outputs
b_farm_list1 <- b_farm_Priming_scenarios[[1]]
# choose only NPV
b_farm_list1 <- b_farm_list1[1:7]

```

### VIP


```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

#PLS
Priming_scenarios_bfarm <- b_farm_Priming_scenarios
Priming_scenarios_bfarm$x<-Priming_scenarios_bfarm$x[,which(!colnames(Priming_scenarios_bfarm$x)=="Scenario")]

#legend_table<-read.csv("Final_Report/baseline.csv", fileEncoding = "UTF-8-BOM")

#PLS for Heat priming - no priming under control
pls_out_bfarm<-plsr.mcSimulation(object=Priming_scenarios_bfarm, 
                                 resultName = names(Priming_scenarios_bfarm$y)[12])


coeff1 <- pls_out_bfarm[["coefficients"]][,,1]
scale  <- pls_out_bfarm[["scale"]]



```

### EVPI & VIP no priming & heat priming wihtout stress treatment

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

# vergleich kk zu HK
b_farm_list14 <- b_farm_list1[c(1,4)]

b_farm_EVPI14 <-  evpi::multi_evppi(b_farm_list2, b_farm_list14)

b_farm_EVPI14 <- data.frame(
  Variable = colnames(b_farm_list2),
  EVPI = b_farm_EVPI14
)


b_farm_EVPI_14 <- b_farm_EVPI14[1:26, ]

VIP_table_HK_KK_bfarm_14 <- data.frame(
  name = names(scale),
  VIP = as.numeric(scale),
  coefficient = as.numeric(coeff1),
EVPI = as.numeric(b_farm_EVPI_14$EVPI))

VIP_table_HK_KK_bfarm14 <- VIP_table_HK_KK_bfarm_14[-26, ]

```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_subset_bfarm14 <- subset(VIP_table_HK_KK_bfarm14,VIP_table_HK_KK_bfarm14$VIP>=0.8)
pls_subset_bfarm14 <- subset(VIP_table_HK_KK_bfarm14,VIP_table_HK_KK_bfarm14$EVPI>=1)
pls_subset_bfarm14$Category[pls_subset_bfarm14$coefficient > 0] = "cadetblue"
pls_subset_bfarm14$Category[pls_subset_bfarm14$coefficient < 0] = "firebrick"
pls_subset_bfarm14$Category[pls_subset_bfarm14$VIP < 1] ="grey"
pls_dat_bfarm14 <- as.data.frame(pls_subset_bfarm14)
name_mapping <- c(
  "Yield_type_4" = "Yield of Heat primed tomato [kg/m2]",
  "Yield_type_7" = "Yield of Salt primed tomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed tomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_bfarm14$X <- name_mapping[pls_dat_bfarm14$name]

p <- ggplot(pls_dat_bfarm14,aes(x=pls_dat_bfarm14$name,y=pls_dat_bfarm14$VIP))+
  geom_bar(aes(fill=pls_dat_bfarm14$Category),stat ="identity")+
  ggtitle("Variable Importance")+
  ylab("VIP scores")+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q <-  ggplot(data = pls_dat_bfarm14, aes(x = pls_dat_bfarm14$X, y = pls_dat_bfarm14$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle("Value of Information") +
  ylab("EVPI")+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()
g.mid <- ggplot(pls_dat_bfarm14,aes(x=1,y=pls_dat_bfarm14$X))+geom_text(aes(label=pls_dat_bfarm14$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_bfarm14$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_bfarm14$X))+
  ggtitle("")+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1 <- ggplot_gtable(ggplot_build(p))
gg2 <- ggplot_gtable(ggplot_build(q))
gg.mid <- ggplot_gtable(ggplot_build(g.mid))
gg_HK_KK_bfarm <- cowplot::plot_grid(gg1,gg.mid,gg2, ncol = 3, align = "h")



```


### EVPI & VIP no priming & salt priming wihtout stress treatment

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
# vergleich kk zu HK
b_farm_list17 <- b_farm_list1[c(1,7)]

b_farm_EVPI17 <-  evpi::multi_evppi(b_farm_list2, b_farm_list17)

b_farm_EVPI17 <- data.frame(
  Variable = colnames(b_farm_list2),
  EVPI = b_farm_EVPI17
)



b_farm_EVPI_17 <- b_farm_EVPI17[1:26, ]

VIP_table_HK_KK_bfarm_17 <- data.frame(
  name = names(scale),
  VIP = as.numeric(scale),
  coefficient = as.numeric(coeff1),
EVPI = as.numeric(b_farm_EVPI_17$EVPI))

VIP_table_HK_KK_bfarm_17 <- VIP_table_HK_KK_bfarm_17[-26, ]

```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_subset_bfarm17 <- subset(VIP_table_HK_KK_bfarm_17,VIP_table_HK_KK_bfarm_17$VIP>=0.8)
pls_subset_bfarm17 <- subset(VIP_table_HK_KK_bfarm_17,VIP_table_HK_KK_bfarm_17$EVPI>=1.1)
pls_subset_bfarm17$Category[pls_subset_bfarm17$coefficient > 0] = "cadetblue"
pls_subset_bfarm17$Category[pls_subset_bfarm17$coefficient < 0] = "firebrick"
pls_subset_bfarm17$Category[pls_subset_bfarm17$VIP < 1] ="grey"
pls_dat_bfarm17 <- as.data.frame(pls_subset_bfarm17)
name_mapping <- c(
  "Yield_type_4" = "Yield of Heat primed tomato [kg/m2]",
  "Yield_type_7" = "Yield of Salt primed tomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed tomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_bfarm17$X <- name_mapping[pls_dat_bfarm17$name]

p <- ggplot(pls_dat_bfarm17,aes(x=pls_dat_bfarm17$name,y=pls_dat_bfarm17$VIP))+
  geom_bar(aes(fill=pls_dat_bfarm17$Category),stat ="identity")+
  ggtitle("Variable Importance")+
  ylab("VIP scores")+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q <-  ggplot(data = pls_dat_bfarm17, aes(x = pls_dat_bfarm17$X, y = pls_dat_bfarm17$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle("Value of Information") +
  ylab("EVPI")+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()
g.mid <- ggplot(pls_dat_bfarm17,aes(x=1,y=pls_dat_bfarm17$X))+geom_text(aes(label=pls_dat_bfarm17$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_bfarm17$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_bfarm17$X))+
  ggtitle("")+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1 <- ggplot_gtable(ggplot_build(p))
gg2 <- ggplot_gtable(ggplot_build(q))
gg.mid <- ggplot_gtable(ggplot_build(g.mid))
gg_SK_KK_bfarm <- cowplot::plot_grid(gg1,gg.mid,gg2, ncol = 3, align = "h")



```


# all farms together 
```{r function, include=FALSE}
set.seed(42)

Priming_input_table <- read_csv("data/baseline.csv")

Priming_simulation <-   mcSimulation(estimate =
                                      estimate_read_csv("data/baseline.csv"),
                                     model_function=Priming_function,
                                     numberOfModelRuns=10000,
                                     functionSyntax="plainNames")
```

## distributions of the mc simulation

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
no_stress_heat <- plot_distributions(mcSimulation_object = Priming_simulation, 
                   vars = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   new_names = c("No Priming","Heat Priming", 
                                 "Salt Priming"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress ")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
  values = c("No Priming" = "#009E73",  "Heat Priming" = "tomato", "Salt Priming" = "#56B4E9"),
    breaks = c("No Priming","Heat Priming", 
                                 "Salt Priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("No Priming","Heat Priming", 
                                 "Salt Priming"))  # << critical: y-axis order




no_stress_salt <- plot_distributions(mcSimulation_object = Priming_simulation, 
                   vars = c("K_K_NPV","S_K_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","S_K_NPV"),
                   new_names = c("no priming","salt priming"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9"),
    breaks = c("no priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("salt priming","no priming"))  # << critical: y-axis order



heat_stress <- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV", "H_H_NPV", "S_H_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress for bigger Farms") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9", "heat priming" = "tomato"),
    breaks = c("no priming",  "salt priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order

heat_stress_heat<- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_H_NPV", "H_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV", "H_H_NPV"),
  new_names = c("no priming", "heat priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73",  "heat priming" = "tomato"),
    breaks = c("no priming",  "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "no priming"))  # << critical: y-axis order



heat_stress_salt <- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_H_NPV", "S_H_NPV"),
  method = 'boxplot', 
  old_names = c("K_H_NPV","S_H_NPV"),
  new_names = c("no priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9"),
    breaks = c("no priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("salt priming","no priming"))  # << critical: y-axis order



salt_stress <- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  method = 'boxplot', 
  old_names = c("K_S_NPV", "H_S_NPV", "S_S_NPV"),
  new_names = c("no priming", "heat priming", "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9", "heat priming" = "tomato"),
    breaks = c("no priming",  "salt priming", "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "salt priming","no priming"))  # << critical: y-axis order

salt_stress_heat <- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_S_NPV", "H_S_NPV"),
  method = 'boxplot', 
  old_names = c("K_S_NPV", "H_S_NPV"),
  new_names = c("no priming", "heat priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73",  "heat priming" = "tomato"),
    breaks = c("no priming",   "heat priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("heat priming", "no priming"))  # << critical: y-axis order



salt_stress_salt <- plot_distributions(
  mcSimulation_object = Priming_simulation, 
  vars = c("K_S_NPV", "S_S_NPV"),
  method = 'boxplot', 
  old_names = c("K_S_NPV", "S_S_NPV"),
  new_names = c("no priming",  "salt priming"),
  base_size = 10,
  legend.position = "none") +
  labs(title = "NPV Distribution with different priming \nunder heat stress") +
  theme_bw() +
  theme( plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(
  values = c("no priming" = "#009E73", "salt priming" = "#56B4E9"),
    breaks = c("no priming",  "salt priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("salt priming","no priming"))  # << critical: y-axis order





cashflow_HK_KK<- plot_cashflow(mcSimulation_object = Priming_simulation, 
              cashflow_var_name = "Cashflow_HK_KK",
              facet_labels = "Cash Flow Comparison Between No Priming \nand Heat Priming" )



cashflow_SK_KK <- plot_cashflow(mcSimulation_object = Priming_simulation, 
              cashflow_var_name = "Cashflow_SK_KK",
              facet_labels ="Cash Flow Comparison Between No Priming \nand Salt Priming" )


no_stress_heat_1 <- plot_distributions(mcSimulation_object = Priming_simulation, 
                   vars = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   method = 'boxplot', 
                   old_names = c("K_K_NPV","H_K_NPV","S_K_NPV"),
                   new_names = c("No Priming","Heat Priming", 
                                 "Salt Priming"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "NPV Distribution with Different Decision Options \nand no stress ")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
  values = c("No Priming" = "#009E73",  "Heat Priming" = "tomato", "Salt Priming" = "#56B4E9"),
    breaks = c("No Priming","Heat Priming", 
                                 "Salt Priming"))+ # order y-axis and legend
  scale_y_discrete(limits = c("Salt Priming","Heat Priming", 
                                 "No Priming"))  # << critical: y-axis order


plot_distributions(mcSimulation_object = Priming_simulation, 
                   vars = c("NPV_H_K_NPV_K_K","NPV_S_K_NPV_K_K"),
                   method = 'boxplot', 
                   old_names = c("NPV_H_K_NPV_K_K","NPV_S_K_NPV_K_K"),
                   new_names = c("(No Priming - Heat Priming)",
                                 "(No Priming - Salt Priming)"),
                   base_size = 10,
                   legend.position = "none") +
  labs(title = "Distribution of NPV Differences between \nNo Priming and Heat or Salt Priming")+
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_manual(
    values = c( "(No Priming - Heat Priming)" = "#ff876e", 
                "(No Priming - Salt Priming)" = "#7cc3ee"),
    breaks = c("(No Priming - Heat Priming)",
               "(No Priming - Salt Priming)"))+ # order y-axis and legend
  scale_y_discrete(limits = c("(No Priming - Heat Priming)",
                              "(No Priming - Salt Priming)"))  # << critical: y-axis order




plot_cashflow(mcSimulation_object = Priming_simulation, 
                               cashflow_var_name = "Cashflow_HK_KK",
                               y_axis_name = "Cashflow [€/m²]",
                               facet_labels = "Cash Flow Comparison Between No Priming \nand Heat Priming",
                               base_size = 14)



plot_cashflow(mcSimulation_object = Priming_simulation, 
                                cashflow_var_name = "Cashflow_SK_KK",
                                y_axis_name = "Cashflow [€/m²]",
                                facet_labels ="Cash Flow Comparison Between No Priming \nand Salt Priming",
                                base_size = 14)


```

## EVPI & VIP

### EVPI
```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
### Value of Information (VoI) analysis ###

#here we subset the outputs from the mcSimulation function (y) by selecting the correct variables
# choose this carefully and be sure to run the multi_EVPI only on the variables that the you want
#EVPI = (EOL : Expected Opportunity Loss)

# make a individual data.frame from the scenario data. 

# Monte carlo inputs
all_farm_list2 <- Priming_simulation[[2]]
#remove the row with character (Farm_1, Farm_2...)
all_farm_list2 <- all_farm_list2[1:25]

# Monte Carlo outputs
all_farm_list1 <- Priming_simulation[[1]]
# choose only NPV
all_farm_list1 <- all_farm_list1[1:9]


```

### VIP


```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}
#PLS

Priming_simulation_allfarms <- Priming_simulation
Priming_simulation_allfarms$x<-Priming_simulation_allfarms$x[,which(!colnames(Priming_simulation_allfarms$x)=="Scenario")]

#legend_table<-read.csv("Final_Report/baseline.csv", fileEncoding = "UTF-8-BOM")


```

### EVPI & VIP no priming & heat priming wihtout stress treatment

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

#PLS for Heat priming - no priming under control
pls_out_allfarm14<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[12])


coeff1_allfarm14 <- pls_out_allfarm14[["coefficients"]][,,1]
scale_allfarm14   <- pls_out_allfarm14[["scale"]]

# vergleich kk zu HK
allfarm_list14 <- all_farm_list1[c(1,4)]

all_farm_EVPI14_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list14)

all_farm_EVPI14 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI14_0)

all_farm_EVPI_14 <- all_farm_EVPI14[1:26, ]

VIP_table_HK_KK_allfarm_14 <- data.frame(
  name = names(scale_allfarm14),
  VIP = as.numeric(scale_allfarm14),
  coefficient = as.numeric(coeff1_allfarm14),
  EVPI = as.numeric(all_farm_EVPI_14$EVPI))

VIP_table_HK_KK_allfarm14 <- VIP_table_HK_KK_allfarm_14[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_14 <- subset(VIP_table_HK_KK_allfarm14,VIP_table_HK_KK_allfarm14$VIP>=0.8)
pls_subset_14 <- subset(pls_subset_14,pls_subset_14$EVPI>=0.01)
pls_subset_14$Category[pls_subset_14$coefficient > 0] = "cadetblue"
pls_subset_14$Category[pls_subset_14$coefficient < 0] = "firebrick"
pls_subset_14$Category[pls_subset_14$VIP < 1] ="grey"
pls_dat_14 <- as.data.frame(pls_subset_14)
name_mapping <- c(
  "Yield_type_4" = "Yield of heat primed \ntomato",
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed \ntomato",
  "Hummel_Nutzlinge" = "bio. plant protection cost",
  "CO2_H2O_Due" = "CO2, Water and \nFertilizer cost",
  "Arbeit" = "Labor cost",
  "discount_rate" = "Discount Rate")
pls_dat_14$X <- name_mapping[pls_dat_14$name]
pls_dat_14 <- pls_dat_14 %>% drop_na()

p_allfarm_14 <- ggplot(pls_dat_14,aes(x=pls_dat_14$X,y = pls_dat_14$VIP))+
  geom_bar(aes(fill=pls_dat_14$Category),stat ="identity")+
  ggtitle(NULL)+
  ylab(NULL)+
  xlab(NULL)+
scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=15),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size=15),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()

q_allfarm_14 <-  ggplot(data = pls_dat_14, aes(x = pls_dat_14$X, y = pls_dat_14$EVPI))+
  geom_bar(fill = "#ff876e",stat = "identity") +
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=12, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=15),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 1.2),breaks = seq(0, 1.2, by = 0.2))
g.mid_allfarm_14 <- ggplot(pls_dat_14,aes(x=1,y=pls_dat_14$X))+
  geom_text(aes(label=pls_dat_14$X), size = 6)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_14$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_14$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_14 <- ggplot_gtable(ggplot_build(p_allfarm_14))
gg2_14 <- ggplot_gtable(ggplot_build(q_allfarm_14))
gg.mid_14 <- ggplot_gtable(ggplot_build(g.mid_allfarm_14))
gg_HK_KK_afarm <- cowplot::plot_grid(gg1_14,gg.mid_14,gg2_14, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_HK_KK_afarm",".png"), gg_HK_KK_afarm,
# width = 20, height = 12, units = 'cm', dpi = 750)



```



### EVPI & VIP no priming & salt priming wihtout stress treatment

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}


pls_out_allfarm17<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[13])
coeff1_allfarm17 <- pls_out_allfarm17[["coefficients"]][,,1]
scale_allfarm17   <- pls_out_allfarm17[["scale"]]

# vergleich kk zu HK
allfarm_list17 <- all_farm_list1[c(1,7)]

all_farm_EVPI17_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list17)

all_farm_EVPI17 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI17_0)

all_farm_EVPI_17 <- all_farm_EVPI17[1:26, ]

VIP_table_SK_KK_allfarm_17 <- data.frame(
  name = names(scale_allfarm17),
  VIP = as.numeric(scale_allfarm17),
  coefficient = as.numeric(coeff1_allfarm17),
  EVPI = as.numeric(all_farm_EVPI_17$EVPI))

VIP_table_SK_KK_allfarm_17 <- VIP_table_SK_KK_allfarm_17[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_17 <- subset(VIP_table_SK_KK_allfarm_17,VIP_table_SK_KK_allfarm_17$VIP>=0.8)
pls_subset_17 <- subset(pls_subset_17,pls_subset_17$EVPI>=0.01)
pls_subset_17$Category[pls_subset_17$coefficient > 0] = "cadetblue"
pls_subset_17$Category[pls_subset_17$coefficient < 0] = "firebrick"
pls_subset_17$Category[pls_subset_17$VIP < 1] ="grey"
pls_dat_17 <- as.data.frame(pls_subset_17)
name_mapping <- c(
  "Yield_type_7" = "Yield of salt primed \ntomato", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_1" = "Yield of unprimed \ntomato",
  "Hummel_Nutzlinge" = "bio. plant protection cost",
  "CO2_H2O_Due" = "CO2, Water and \nFertilizer cost",
  "Arbeit" = "Labor cost"
  
)
pls_dat_17$X <- name_mapping[pls_dat_17$name]
pls_dat_17 <- pls_dat_17 %>% drop_na()

p_allfarm_17 <- ggplot(pls_dat_17,aes(x=pls_dat_17$X,y=pls_dat_17$VIP))+
  geom_bar(aes(fill=pls_dat_17$Category),stat ="identity")+
  ggtitle(NULL)+
  ylab(NULL)+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()



q_allfarm_17 <-  ggplot(data = pls_dat_17, aes(x = pls_dat_17$X, y = pls_dat_17$EVPI))+
  geom_bar(fill = "#7cc3ee",stat = "identity") +
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=15),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 1.2),breaks = seq(0, 1.2, by = 0.2))
g.mid_allfarm_17 <- ggplot(pls_dat_17,aes(x=1,y=pls_dat_17$X))+
  geom_text(aes(label=pls_dat_17$X), size=6)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_17$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_17$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_17 <- ggplot_gtable(ggplot_build(p_allfarm_17))
gg2_17 <- ggplot_gtable(ggplot_build(q_allfarm_17))
gg.mid_17 <- ggplot_gtable(ggplot_build(g.mid_allfarm_17))
gg_SK_KK_afarm <- cowplot::plot_grid(gg1_17,gg.mid_17,gg2_17, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_SK_KK_afarm",".png"), gg_SK_KK_afarm,
#         width = 20, height = 12, units = 'cm', dpi = 750)



```



### EVPI & VIP no priming & heat priming wiht heat stress

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_out_allfarm25<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[14])


coeff1_allfarm25 <- pls_out_allfarm25[["coefficients"]][,,1]
scale_allfarm25   <- pls_out_allfarm25[["scale"]]

# vergleich kk zu HK
allfarm_list25 <- all_farm_list1[c(2,5)]

all_farm_EVPI25_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list25)

all_farm_EVPI25 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI25_0)

all_farm_EVPI_25 <- all_farm_EVPI25[1:26, ]

VIP_table_allfarm_25 <- data.frame(
  name = names(scale_allfarm25),
  VIP = as.numeric(scale_allfarm25),
  coefficient = as.numeric(coeff1_allfarm25),
  EVPI = as.numeric(all_farm_EVPI_25$EVPI))

VIP_table_allfarm25 <- VIP_table_allfarm_25[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_25 <- subset(VIP_table_allfarm25,VIP_table_allfarm25$VIP>=0.8)
pls_subset_25 <- subset(VIP_table_allfarm25,VIP_table_allfarm25$EVPI>=1)
pls_subset_25$Category[pls_subset_25$coefficient > 0] = "cadetblue"
pls_subset_25$Category[pls_subset_25$coefficient < 0] = "firebrick"
pls_subset_25$Category[pls_subset_25$VIP < 1] ="grey"
pls_dat_25 <- as.data.frame(pls_subset_25)
name_mapping <- c(
  "Yield_type_5" = "Yield of heat primed \ntomato [kg/m2]",
  "Yield_type_8" = "Yield of salt primed \ntomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_2" = "Yield of unprimed \ntomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_25$X <- name_mapping[pls_dat_25$name]

p_allfarm_25 <- ggplot(pls_dat_25,aes(x=pls_dat_25$X,y=pls_dat_25$VIP))+
  geom_bar(aes(fill=pls_dat_25$Category),stat ="identity")+
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q_allfarm_25 <-  ggplot(data = pls_dat_25, aes(x = pls_dat_25$X, y = pls_dat_25$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 15),breaks = seq(0, 15, by = 3))
g.mid_allfarm_25 <- ggplot(pls_dat_25,aes(x=1,y=pls_dat_25$X))+
  geom_text(aes(label=pls_dat_25$X), size = 7)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_25$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_25$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_25 <- ggplot_gtable(ggplot_build(p_allfarm_25))
gg2_25 <- ggplot_gtable(ggplot_build(q_allfarm_25))
gg.mid_25 <- ggplot_gtable(ggplot_build(g.mid_allfarm_25))
gg_KH_HH_afarm <- cowplot::plot_grid(gg1_25,gg.mid_25,gg2_25, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_KH_HH_afarm",".png"), gg_KH_HH_afarm,
#         width = 20, height = 10, units = 'cm', dpi = 750)



```



### EVPI & VIP no priming & salt priming wiht heat stress

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_out_allfarm28<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[15])


coeff1_allfarm28 <- pls_out_allfarm28[["coefficients"]][,,1]
scale_allfarm28   <- pls_out_allfarm28[["scale"]]

# vergleich kk zu HK
allfarm_list28 <- all_farm_list1[c(2,8)]

all_farm_EVPI28_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list28)

all_farm_EVPI28 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI28_0)

all_farm_EVPI_28 <- all_farm_EVPI28[1:26, ]

VIP_table_allfarm_28 <- data.frame(
  name = names(scale_allfarm28),
  VIP = as.numeric(scale_allfarm28),
  coefficient = as.numeric(coeff1_allfarm28),
 EVPI = as.numeric(all_farm_EVPI_28$EVPI))

VIP_table_allfarm28 <- VIP_table_allfarm_28[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_28 <- subset(VIP_table_allfarm28,VIP_table_allfarm28$VIP>=0.8)
pls_subset_28 <- subset(VIP_table_allfarm28,VIP_table_allfarm28$EVPI>=1)
pls_subset_28$Category[pls_subset_28$coefficient > 0] = "cadetblue"
pls_subset_28$Category[pls_subset_28$coefficient < 0] = "firebrick"
pls_subset_28$Category[pls_subset_28$VIP < 1] ="grey"
pls_dat_28 <- as.data.frame(pls_subset_28)
name_mapping <- c(
  "Yield_type_5" = "Yield of heat primed \ntomato [kg/m2]",
  "Yield_type_8" = "Yield of salt primed \ntomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_2" = "Yield of unprimed \ntomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_28$X <- name_mapping[pls_dat_28$name]

p_allfarm_28 <- ggplot(pls_dat_28,aes(x=pls_dat_28$X,y=pls_dat_28$VIP))+
  geom_bar(aes(fill=pls_dat_28$Category),stat ="identity")+
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q_allfarm_28 <-  ggplot(data = pls_dat_28, aes(x = pls_dat_28$X, y = pls_dat_28$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 15),breaks = seq(0, 15, by = 3))
g.mid_allfarm_28 <- ggplot(pls_dat_28,aes(x=1,y=pls_dat_28$X))+
  geom_text(aes(label=pls_dat_28$X), size = 7)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_28$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_28$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_28 <- ggplot_gtable(ggplot_build(p_allfarm_28))
gg2_28 <- ggplot_gtable(ggplot_build(q_allfarm_28))
gg.mid_28 <- ggplot_gtable(ggplot_build(g.mid_allfarm_28))
gg_SH_KH_afarm <- cowplot::plot_grid(gg1_28,gg.mid_28,gg2_28, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_SH_KH_afarm",".png"), gg_SH_KH_afarm,
#         width = 20, height = 10, units = 'cm', dpi = 750)



```



### EVPI & VIP no priming & heat priming wiht salt stress

data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_out_allfarm36<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[16])


coeff1_allfarm36 <- pls_out_allfarm36[["coefficients"]][,,1]
scale_allfarm36   <- pls_out_allfarm36[["scale"]]

# vergleich kk zu HK
allfarm_list36 <- all_farm_list1[c(3,6)]

all_farm_EVPI36_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list36)

all_farm_EVPI36 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI36_0)

all_farm_EVPI_36 <- all_farm_EVPI36[1:26, ]

VIP_table_allfarm_36 <- data.frame(
  name = names(scale_allfarm36),
  VIP = as.numeric(scale_allfarm36),
  coefficient = as.numeric(coeff1_allfarm36),
EVPI = as.numeric(all_farm_EVPI_36$EVPI))

VIP_table_allfarm36 <- VIP_table_allfarm_36[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_36 <- subset(VIP_table_allfarm36,VIP_table_allfarm36$VIP>=0.8)
pls_subset_36 <- subset(VIP_table_allfarm36,VIP_table_allfarm36$EVPI>=1)
pls_subset_36$Category[pls_subset_36$coefficient > 0] = "cadetblue"
pls_subset_36$Category[pls_subset_36$coefficient < 0] = "firebrick"
pls_subset_36$Category[pls_subset_36$VIP < 1] ="grey"
pls_dat_36 <- as.data.frame(pls_subset_36)
name_mapping <- c(
  "Yield_type_6" = "Yield of heat primed \ntomato [kg/m2]",
  "Yield_type_9" = "Yield of salt primed \ntomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_3" = "Yield of unprimed \ntomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_36$X <- name_mapping[pls_dat_36$name]

p_allfarm_36 <- ggplot(pls_dat_36,aes(x=pls_dat_36$X,y=pls_dat_36$VIP))+
  geom_bar(aes(fill=pls_dat_36$Category),stat ="identity")+
   ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q_allfarm_36 <-  ggplot(data = pls_dat_36, aes(x = pls_dat_36$X, y = pls_dat_36$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
   ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 15),breaks = seq(0, 15, by = 3))
g.mid_allfarm_36 <- ggplot(pls_dat_36,aes(x=1,y=pls_dat_36$X))+
  geom_text(aes(label=pls_dat_36$X), size = 7)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_36$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_36$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_36 <- ggplot_gtable(ggplot_build(p_allfarm_36))
gg2_36 <- ggplot_gtable(ggplot_build(q_allfarm_36))
gg.mid_36 <- ggplot_gtable(ggplot_build(g.mid_allfarm_36))
gg_HS_KS_afarm <- cowplot::plot_grid(gg1_36,gg.mid_36,gg2_36, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_HS_KS_afarm",".png"), gg_HS_KS_afarm,
#         width = 20, height = 10, units = 'cm', dpi = 750)



```


### EVPI & VIP no priming & salt priming wiht salt stress
data frame for EVPIs and VIPs

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 5, fig.align = "center"}

pls_out_allfarm39<-plsr.mcSimulation(object=Priming_simulation_allfarms, 
                                 resultName = names(Priming_simulation_allfarms$y)[17])


coeff1_allfarm39 <- pls_out_allfarm39[["coefficients"]][,,1]
scale_allfarm39   <- pls_out_allfarm39[["scale"]]

# vergleich kk zu HK
allfarm_list39 <- all_farm_list1[c(3,9)]

all_farm_EVPI39_0 <-  evpi::multi_evppi(all_farm_list2, allfarm_list39)

all_farm_EVPI39 <- data.frame(
  Variable = colnames(all_farm_list2),
  EVPI = all_farm_EVPI39_0)

all_farm_EVPI_39 <- all_farm_EVPI39[1:26, ]

VIP_table_allfarm_39 <- data.frame(
  name = names(scale_allfarm39),
  VIP = as.numeric(scale_allfarm39),
  coefficient = as.numeric(coeff1_allfarm39), 
  EVPI = as.numeric(all_farm_EVPI_39$EVPI))

VIP_table_allfarm39 <- VIP_table_allfarm_39[-26, ]


```

graphs 

```{r ,echo=T, warning=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
pls_subset_39 <- subset(VIP_table_allfarm39,VIP_table_allfarm39$VIP>=0.8)
pls_subset_39 <- subset(VIP_table_allfarm39,VIP_table_allfarm39$EVPI>=1)
pls_subset_39$Category[pls_subset_39$coefficient > 0] = "cadetblue"
pls_subset_39$Category[pls_subset_39$coefficient < 0] = "firebrick"
pls_subset_39$Category[pls_subset_39$VIP < 1] ="grey"
pls_dat_39 <- as.data.frame(pls_subset_39)
name_mapping <- c(
  "Yield_type_6" = "Yield of heat primed \ntomato [kg/m2]",
  "Yield_type_9" = "Yield of salt primed \ntomato [kg/m2]", 
  "Jungepflanzen_Priming" = "primed seedling cost",
  "Yield_type_3" = "Yield of unprimed \ntomato [kg/m2]",
  "Hummel_Nutzlinge" = "bio. plant protection cost [€/m2]"
)
pls_dat_39$X <- name_mapping[pls_dat_39$name]

p_allfarm_39 <- ggplot(pls_dat_39,aes(x=pls_dat_39$X,y=pls_dat_39$VIP))+
  geom_bar(aes(fill=pls_dat_39$Category),stat ="identity")+
 ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  scale_fill_manual(values = c("cadetblue","firebrick","grey"))+
  theme(axis.title.y =element_text(color="black", size=8),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,-1,1,0), "mm")) +
  geom_hline(yintercept = 1, size=0.2)+
  theme(legend.position = "none")+
  scale_y_reverse() +
  coord_flip()
q_allfarm_39 <-  ggplot(data = pls_dat_39, aes(x = pls_dat_39$X, y = pls_dat_39$EVPI))+
  geom_bar(fill = "deepskyblue3",stat = "identity") +
  ggtitle(NULL) +
  ylab(NULL)+
  xlab(NULL)+
  theme(axis.title.y = element_text(color="black", size=8, face = "bold"),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(1,0,1,-1), "mm")) +
  coord_flip()+
  scale_y_continuous(limits = c(0, 15),breaks = seq(0, 15, by = 3))
g.mid_allfarm_39 <- ggplot(pls_dat_39,aes(x=1,y=pls_dat_39$X))+
  geom_text(aes(label=pls_dat_39$X), size=4)+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_39$X))+
  geom_segment(aes(x=0,xend=0,yend=pls_dat_39$X))+
  ggtitle(NULL)+
  ylab(NULL)+
  scale_x_continuous(expand=c(0,0),limits=c(1.0,1.0))+
  theme(axis.title=element_blank(),
        panel.grid=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.background=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.margin = unit(c(1,0,1,0), "mm"))

gg1_39 <- ggplot_gtable(ggplot_build(p_allfarm_39))
gg2_39 <- ggplot_gtable(ggplot_build(q_allfarm_39))
gg.mid_39 <- ggplot_gtable(ggplot_build(g.mid_allfarm_39))
gg_SS_KS_afarm <- cowplot::plot_grid(gg1_39,gg.mid_39,gg2_39, ncol = 3, align = "h")

# ggsave( paste0("graphs/all_farms/gg_SS_KS_afarm",".png"), gg_SS_KS_afarm,
#         width = 20, height = 10, units = 'cm', dpi = 750)



```





### citation 

```{r, include=FALSE}
knitr::write_bib(c("evpi", "decisionSupport"), "packages.bib")
```
